Long Term Monitoring of the Disintegrating Planet Candidate KIC 12557548 b

### 2017-07-20 ms.tex
Smoothed out the wording in the intro and added some phrases about the high resolution spectroscopy.

\begin{abstract}
KIC 12557548 b is one of several disintegrating planet candidates which lose mass in the form of dust particles escaping their surface. Photometric monitoring of KIC 12557548 b originally showed evidence for a slowdown of integration activity in 2013 and 2014. Here, we report 2016 measurements that are consistent with photometry from the Kepler spacecraft in 2009-2013.
\end{abstract}

@@

\section{Introduction}
\citet{rappaport} first reported the discovery of a highly unusual stellar system in the Kepler field.
KIC 12557548's (hereafter \shStar's) light curve exhibited periodic flux dips with a period of 0.653 days.
What was highly unusual about \shStar\ was that the flux dips were neither symmetric in shape nor constant in amplitude, varying from $\sim$ 0\% to $\sim$ 1.2\%.
The variations in amplitude are highly stochastic and unpredictable from one event to the next 0.653 days later.
This indicates the creation and clearing of material that can cover up to 1\% of the star in $\lesssim$ 1 day timescales.
These variable dips are best explained as dust extinction from material that is escaping a rocky planet (KIC 12557548 b, hereafter \sha) in a short period orbit.
The \shStar\ system has the exciting possibility of being an opportunity to study a planet that has been peeled away layer by layer to reveal an interior core.

@@

Furthermore, there are perplexing systems that also display stochastic transit behavior but for which there are still no agreed-upon explanations: KIC 8462852 (ie. Boyajian's star) \citep{boyajian846}, RIK-210 \citep{david2017rik210} and PTFO 8-8695 \citep{vanEyken2012ptfTTauri}.
KIC 8462852 may be a family of comets from one or more parent bodies that recently were broken apart.
RIK-210 and PTFO 8-8695 are both in young systems ($\lesssim$ 10 and $\lesssim$3 Myr respectively) so they may be proto-planets.
RIK-210 may have accreting material that causes variable extinction.
PTFO 8-8695's orbit may be precessing and causing variations in transit depth depending on its longitude.

Observational evidence from the \shStar\ system puts constraints on the planet candidate on the system.
Radial velocity velocity variations of the host star put an upper limit on the reflex motion due to the planet and constrains the mass to be $\lesssim 1.2 M_{\mathrm Jup}$ \citep{croll2014}.
There is no detection of secondary eclipses of \sha\ with a 3$\sigma$ upper limit of $5 \times 10^{-5}$ in the Kepler bandpass, which means that for an albedo of 0.5, the radius of the planet must be smaller than 4600 km.
The timescale of the variability of the transits gives a mass lot rate of order $\sim M_\oplus/Gyr$, which would indicate a present-day mass of 0.014 $M_\oplus$ when using a radiative-hydrodynamic wind model \citep{perez-becker}.

@@

Subsequently, \citet{schlawin2016kic1255} observed 8 total transits of the system for 4 nights in 2013 and 4 nights in 2014 for the $r'$ band using the MORIS imager \citep{Gulbis2011} on SpeX/IRTF \citep{rayner03}.
\citet{schlawin2016kic1255} found that the transit depths were all weaker than $0.43\%$ and that the probably of this randomly occurring based on random behavior from Kepler statistics was around 0.2\%.
This was evidence that the observations occured during weaker periods (as found in \citet{vanWerkhoven2014}'s 15 Kepler quarter analysis) or that the disintegration activity was falling off with time.
We performed follow-up $R$ band photometry of the \shStar\ system to explore whether the disintegration activity is shutting off with time.

@@

\begin{figure}[!hbtp]
\begin{centering}
\includegraphics[width=0.45\textwidth]{images/subaru/bosz_mg_triplet.pdf}
\caption{Example spectrum of \shStar\ (reduced by Kento Mashuda) near the Mg triplet compared to 4500 K BOSZ models with two different log(g)s.}\label{fig:mgTriplet}
\end{centering}
\end{figure}

>>>>

\begin{abstract}
KIC 12557548 b is one of several disintegrating planet candidates which lose mass in the form of dust particles escaping their surface. Photometric monitoring of KIC 12557548 b originally showed evidence for a slowdown of integration activity in 2013 and 2014. Here, we report 2016 measurements that are consistent with photometry from the Kepler spacecraft in 2009-2013.
We also examine the system with high resolution spectroscopy and discuss the parameters of the host star.
\end{abstract}

@@

\section{Introduction}
\citet{rappaport} first reported the discovery of a highly unusual stellar system in the Kepler field.
KIC 12557548's (hereafter \shStar's) light curve exhibits periodic flux dips with a period of 0.653 days.
Surprisingly, the flux dips are neither symmetric in shape nor constant in amplitude, varying from $\sim$ 0\% to $\sim$ 1.2\%.
The amplitudes of the flux dips are highly stochastic and unpredictable from one event to the next 0.653 days later.
This indicates the creation and clearing of material that can cover up to 1\% of the star in $\lesssim$ 1 day timescales.
These unusual light curve behaviors are best explained as dust extinction from material that is escaping a rocky planet (KIC 12557548 b, hereafter \sha) in a short period orbit.
The \shStar\ system has the exciting possibility of being an opportunity to study a planet that has been peeled away layer by layer to reveal an interior core.

@@

Furthermore, there are perplexing systems that also display stochastic transit behavior but for which there are still no agreed-upon explanations: KIC 8462852 (ie. Boyajian's star) \citep{boyajian846}, RIK-210 \citep{david2017rik210} and PTFO 8-8695 \citep{vanEyken2012ptfTTauri}.
KIC 8462852 may be a family of comets from one or more parent bodies that recently were broken apart.
RIK-210 and PTFO 8-8695 are both in young systems ($\lesssim$ 10 and $\lesssim$3 Myr respectively) so they may are proto-planet candidates.
RIK-210 may have accreting material that causes variable extinction while PTFO 8-8695's orbit may be precessing and causing variations in transit depth depending on its longitude.

The underlying planet candidate \sha\ has not been detected directly, but several observational constraints have placed upper limits on its size and mass.
High precision radial velocity measurements of the host star put an upper limit on the reflex motion due to the planet and constrains the mass to be $\lesssim 1.2 M_{\mathrm Jup}$ \citep{croll2014}.
There is no detection of secondary eclipses of \sha\ with a 3$\sigma$ upper limit of $5 \times 10^{-5}$ in the Kepler bandpass, which means that for an albedo of 0.5, the radius of the planet must be smaller than 4600 km \citep{vanWerkhoven2014}.
The timescale of the variability of the transits gives a mass lot rate of order $\sim M_\oplus/Gyr$, which would indicate a present-day mass of 0.014 $M_\oplus$ when using a radiative-hydrodynamic wind model \citep{perez-becker}.

@@

Subsequently, \citet{schlawin2016kic1255} observed 8 total transits of the system for 4 nights in 2013 and 4 nights in 2014 for the $r'$ band using the MORIS imager \citep{Gulbis2011} on SpeX/IRTF \citep{rayner03}.
\citet{schlawin2016kic1255} found that the transit depths were all weaker than $0.43\%$ and that the probably of this randomly occurring based on random behavior from Kepler statistics was around 0.2\%.
This was evidence that the observations occured during weaker periods (as found in \citet{vanWerkhoven2014}'s 15 Kepler quarter analysis) or that the disintegration activity was falling off with time.
We performed follow-up $R$ band photometry of the \shStar\ system to explore whether the disintegration activity is shutting off with time.
We also analyze high resolution spectroscopy of the system to help resolve some of the different stellar parameters reported in the literature.

@@

\begin{figure}[!hbtp]
\begin{centering}
\includegraphics[width=0.45\textwidth]{images/subaru/bosz_mg_triplet.pdf}
\caption{Example spectrum of \shStar\ (reduced by Kento Masuda) near the Mg triplet compared to 4500 K BOSZ models with two different log(g)s.}\label{fig:mgTriplet}
\end{centering}
\end{figure}
